The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-09-25 manuscript.Rmd
[fix #59] compute median number of cells occupied by species
and plot species rank abundance based on number of cells they occupy
[fix #65] improve figure legends where needed

```{r compare_database_coverage, fig.cap='Overlap between the regional species list (list), records in iDigBio (idigbio), records in OBIS (obis), and records in BOLD (bold) for the Gulf of Mexico (left) and the Pacific Northwest (right). This plot is generated using the UpSet technique[@Lex2014;@Conway2017], which uses a matrix-based layout to represent intersections of sets and their sizes. The rows represent the sets, the columns represent the intersections, and each set that is part of the intersection is marked with a black-filled circle in the cells underneath. Black lines connect the sets that are part of the intersections. (\\#fig:database-coverage)', echo=FALSE}
knitr::include_graphics("figures/database_coverage.pdf")
```

@@

```{r compare_database_overlap, fig.cap='Proportions of the total number of species by phylum that are absent from faunistic lists but are in iDigBio or OBIS ("Not in list"), and absent from iDigBio or OBIS but are in the faunistic lists ("Not in databases"). The numbers represent the number of species. (\\#fig:database-overlap)'}
knitr::include_graphics("figures/database_overlap_percent.pdf")
```

@@

@@

```{r id_though_time, fig.cap='Proportion of marine invertebrate specimens collected through time identified at the species level. Trend lines are  B-splines of the 3rd degree polynomial. For all groups, we observe a decline in the proportion of specimens collected identified at the species level suggesting a lack of expertise to identify precisely what is collected. (\\#fig:identification-through-time)'}
knitr::include_graphics("figures/idigbio_identification_level_through_time.pdf")
```

@@

>>>>

```{r compare_database_coverage, fig.cap='Overlap between the regional species list (list), records in iDigBio (idigbio), records in OBIS (obis), and records in BOLD (bold) for the Gulf of Mexico (left) and the Pacific Northwest (right). A higher proportion of species in the regional checklists are captured in databases for the Gulf of Mexico compared with the Pacific Northwest. This plot is generated using the UpSet technique[@Lex2014;@Conway2017], which uses a matrix-based layout to represent intersections of sets and their sizes. The rows represent the sets, the columns represent the intersections, and each set that is part of the intersection is marked with a black-filled circle in the cells underneath. Black lines connect the sets that are part of the intersections. (\\#fig:database-coverage)', echo=FALSE}
knitr::include_graphics("figures/database_coverage.pdf")
```

@@

```{r compare_database_overlap, fig.cap='Proportions of the total number of species by phylum that are absent from faunistic lists but are in iDigBio or OBIS ("Not in list"), and absent from iDigBio or OBIS but are in the faunistic lists ("Not in databases"). Many species, even in diverse taxonomic groups, known to occur in these regions have no digital records. The numbers represent the number of species. (\\#fig:database-overlap)'}
knitr::include_graphics("figures/database_overlap_percent.pdf")
```

@@

The median number of cells occupied by species is `r median(rastercell_distribution$n_cell)`.

@@

```{r id_though_time, fig.cap='Proportion of marine invertebrate specimens collected through time identified at the species level. Trend lines are  B-splines of the 3rd degree polynomial. For all groups, we observe a decline in the proportion of specimens collected identified at the species leveld. (\\#fig:identification-through-time)'}
knitr::include_graphics("figures/idigbio_identification_level_through_time.pdf")
```

@@

```{r rank-abundance, fig.cap="Rank abundance plots for most represented phyla."}
knitr::include_graphics("figures/rank_abundance.pdf")
```
